Capstone Movielens Report

### 2025-12-25 reports/capstone-movielens.site/02.5.UME-model.Rmd
Report refactoring: Model Regularization sections.

We begin this section with the concept's mathematical description presented below in the subsection [UME Model Regularization: Mathematical Description].

@@

2. **Fine-tuning:** (Described in the subsection [UME Model Regularization: Fine-tuning]) Determining the best value of $\lambda$ with the highest possible accuracy that minimizes the *RMSE* score for the model.

  3. **Retraining:** (Described in subsection [UME Model Regularization: Retraining the Model with the best $\lambda$]) Retraining the model with the best value of $\lambda$ determined in the previous step.

#### UME Model Regularization: Mathematical Description
\

@@

#### UME Model Regularization: Fine-tuning
\

@@

#### UME Model Regularization: Retraining the Model with the best $\lambda$
\

>>>>

We begin this section with the concept's mathematical description presented below in the subsection [UME Model Regularization: *Mathematical Description*].

@@

2. **Fine-tuning:** (Described in the subsection [UME Model Regularization: *Fine-tuning*]) Determining the best value of $\lambda$ with the highest possible accuracy that minimizes the *RMSE* score for the model.

  3. **Retraining:** (Described in subsection [UME Model Regularization: *Retraining the Model with the best* $\lambda$]) Retraining the model with the best value of $\lambda$ determined in the previous step.

#### UME Model Regularization: *Mathematical Description*
\

@@

#### UME Model Regularization: *Fine-tuning*
\

@@

#### UME Model Regularization: *Retraining the Model with the best* $\lambda$
\

### 2025-12-25 reports/capstone-movielens.site/02.6.UMGE-model.Rmd
Report refactoring: Model Regularization sections.

#### UMGE Model Regularization: Mathematical Description
\

@@

As we decided earlier (and outlined in the [UME Model Regularization] section), we implement the *Regularization method* for our models in the following three steps:

  1. **Pre-configuration:** Preliminary determination of the optimal range of *regularization parameter* $\lambda$ values for the *K-Fold Cross-Validation* samples, where the $K$ is the length of the [`edx_CV` Object] (described in detail in [Appendix B: Models Training Datasets]) to which the *K-Fold Cross-Validation* is applied (in *this Project* we use $K = 5$);

  2. **Fine-tuning:** Figuring out the best value of $\lambda$ with the highest possible accuracy that minimizes the *RMSE* of the model.

  3. **Retraining:** Retraining the model with the best value of $\lambda$ determined in the previous step.

@@

#### UMGE Model Regularization: Pre-configuration
\

@@

#### UMGE Model Regularization: Fine-tuning
\

@@

#### UMGE Model Regularization: Retraining the Model with the best $\lambda$
\

>>>>

We begin this section with the concept's mathematical description presented below in the subsection [UMGE Model Regularization: *Mathematical Description*].

Next, we will implement the *UMGE Model Regularization* in the following three steps:

  1. **Pre-configuration:** (Described in subsection [UMGE Model Regularization: *Pre-configuration*]) Preliminary determination of the optimal range of *regularization parameter* $\lambda$ values for the *K-Fold Cross-Validation* samples, where the $K$ is the length of the [`edx_CV` Object] (described in detail in [Appendix B: Models Training Datasets]) to which the *K-Fold Cross-Validation* is applied (in *this Project* we use $K = 5$);

2. **Fine-tuning:** (Described in the subsection [UMGE Model Regularization: *Fine-tuning*]) Determining the best value of $\lambda$ with the highest possible accuracy that minimizes the *RMSE* score for the model.

  3. **Retraining:** (Described in subsection [UMGE Model Regularization: *Retraining the Model with the best* $\lambda$]) Retraining the model with the best value of $\lambda$ determined in the previous step.

#### UMGE Model Regularization: *Mathematical Description*
\

@@

@@

#### UMGE Model Regularization: *Pre-configuration*
\

@@

#### UMGE Model Regularization: *Fine-tuning*
\

@@

#### UMGE Model Regularization: *Retraining the Model with the best* $\lambda$
\

### 2025-12-25 reports/capstone-movielens.site/02.7.UMGYE-model.Rmd
Report refactoring: Model Regularization sections.

#### UMGYE Model Regularization: Mathematical Description
\

@@

As with the previous models, we implement the _Regularization_ method for the current model in the following three steps:

  1. **Pre-configuration:** Preliminary determination of the optimal range of $\lambda$ values for the *K-Fold Cross Validation* samples, where the $K$ is the length of the [`edx_CV` Object] (described in detail in [Appendix B: Models Training Datasets]) to which the *K-Fold Cross-Validation* is applied (in *this Project* we use $K = 5$);

  2. **Fine-tuning:** figuring out the value of $\lambda$ that minimizes the model's RMSE.

  3. **Retraining:** retraining the model with the best value of the parameter $\lambda$ obtained in the previous step.

@@

#### UMGYE Model Regularization: Pre-configuration
\

@@

#### UMGYE Model Regularization: Fine-tuning
\

@@

#### UMGYE Model Regularization: Retraining the Model with the best $\lambda$
\

>>>>

We begin this section with the concept's mathematical description presented below in the subsection [UMGYE Model Regularization: *Mathematical Description*].

Next, we will implement the *UME Model Regularization* in the following three steps:

  1. **Pre-configuration:** (Described in subsection [UMGYE Model Regularization: *Pre-configuration*]) Preliminary determination of the optimal range of *regularization parameter* $\lambda$ values for the *K-Fold Cross-Validation* samples, where the $K$ is the length of the [`edx_CV` Object] (described in detail in [Appendix B: Models Training Datasets]) to which the *K-Fold Cross-Validation* is applied (in *this Project* we use $K = 5$);

2. **Fine-tuning:** (Described in the subsection [UMGYE Model Regularization: *Fine-tuning*]) Determining the best value of $\lambda$ with the highest possible accuracy that minimizes the *RMSE* score for the model.

  3. **Retraining:** (Described in subsection [UMGYE Model Regularization: *Retraining the Model with the best* $\lambda$]) Retraining the model with the best value of $\lambda$ determined in the previous step.

#### UMGYE Model Regularization: *Mathematical Description*
\

@@

@@

#### UMGYE Model Regularization: *Pre-configuration*
\

@@

#### UMGYE Model Regularization: *Fine-tuning*
\

@@

#### UMGYE Model Regularization: *Retraining the Model with the best* $\lambda$
\

### 2025-12-25 reports/capstone-movielens.site/02.8-0.UMGYDE-model.Rmd
Report refactoring: Model Regularization sections.

#### UMGYDE Model Regularization: Mathematical Description
\

@@

#### UMGYDE Model Regularization: Pre-configuration
\

@@

#### UMGYDE Model Regularization: Fine-tuning
\

@@

#### UMGYDE Model Regularization: Retraining the Model with the best $\lambda$
\

>>>>

We begin this section with the concept's mathematical description presented below in the subsection [UMGYDE Model Regularization: *Mathematical Description*].

Next, we will implement the *UME Model Regularization* in the following three steps:

  1. **Pre-configuration:** (Described in subsection [UMGYDE Model Regularization: *Pre-configuration*]) Preliminary determination of the optimal range of *regularization parameter* $\lambda$ values for the *K-Fold Cross-Validation* samples, where the $K$ is the length of the [`edx_CV` Object] (described in detail in [Appendix B: Models Training Datasets]) to which the *K-Fold Cross-Validation* is applied (in *this Project* we use $K = 5$);

2. **Fine-tuning:** (Described in the subsection [UMGYDE Model Regularization: *Fine-tuning*]) Determining the best value of $\lambda$ with the highest possible accuracy that minimizes the *RMSE* score for the model.

  3. **Retraining:** (Described in subsection [UMGYDE Model Regularization: *Retraining the Model with the best* $\lambda$]) Retraining the model with the best value of $\lambda$ determined in the previous step.

#### UMGYDE Model Regularization: *Mathematical Description*
\

@@

#### UMGYDE Model Regularization: *Pre-configuration*
\

@@

#### UMGYDE Model Regularization: *Fine-tuning*
\

@@

#### UMGYDE Model Regularization: *Retraining the Model with the best* $\lambda$
\
